% !TEX program = xelatex

\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[L]{\textit{Compiled by \XeLaTeX{}}}
\fancyfoot[R]{Last Modified: \today}
\fancyfoot[C]{}
\fancyhead{}

\usepackage{ruby}
\renewcommand{\rubysep}{-0.1ex}

\newcommand{\awardline}[3]{\par \hspace{0em}\rlap{\textit{#1}} \hspace{.25\textwidth}\rlap{#2} \hfill #3 \par}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Qingwen GUAN (\ruby{管}{カン}\,\ruby{清文}{キヨフミ})}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in email address
\contactInfo{qingwen.guan@outlook.com}{(+86) 134 0115 7995}{http://lnked.in/qingwen}
% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}

% Experiences表示经历可数，经验不可数
\section{\faUsers\ Long-term Experiences}
\datedsubsection{\textbf{DiDi Chuxing (Xiaoju Kuaizhi Inc.)} Beijing, China}{2016 -- Present}
\role{Research and Develop Engineer}{DiDi Research}
I am and have been working on many projects, such as
Smart Order Distribution\,(智能分单),
Dynamic Pricing\,(动态调价),
Transport Capacity Dispatch\,(运力调度),
Supply and Demand Forecast\,(供需预测),
Passenger Subsidy\,(乘客补贴),
Thermodynamic Diagram\,(热力图), 
see the Selected Projects Session in the next page for more details.

% data virtualization, and so on.

\datedsubsection{\textbf{Microsoft Inc.} Beijing, China}{2013 -- 2015 (2 yrs)}
\role{Research Intern}{Microsoft Research Asia}
I have been working on many projects, 
such as Document Rectification, Text Detection, Click Through Rate Prediction, Talking and Dancing Robot,
see the Selected Projects Session in the next page for more details.

\section{\faUser\ Short-term Experiences}

\datedsubsection{\textbf{Google Inc.} London, United Kingdom}{Nov.\,2015 -- Jan.\,2016 (3 mos)}
\role{Software Engineer}{Android Google Search App Team}
I was fixing bugs and refactoring code for the Android App of Google Now.

\datedsubsection{\textbf{Toutiao (Bytedance Inc.)} Beijing, China}{Jul.\,2015 -- Nov.\,2015 (4 mos)}
\role{Software Engineer}{Internationalization Team}
I was building the recommendation system module from scratch. 

\datedsubsection{\textbf{J.P. Morgan Chase} Beijing, China}{Jul.\,2014 -- Oct.\,2014 (3 mos)}
\role{Summer Analyst}{Quantitative Research Team}
I was refactoring code and processing data for internal usage.

\section{\faGraduationCap\ Educations}
%\datedsubsection{\textbf{Beihang University (BUAA)}, Beijing, China}{2012 -- 2015 (3 yrs)}
%\textit{Master} in Software Engineering.

%\datedsubsection{\textbf{Beihang University (BUAA)}, Beijing, China}{2008 -- 2012 (4 yrs)}
%\textit{Bachelor} in Software Engineering and Applied Mathematics(minor). 
%\begin{itemize}
%  \item High Scored Courses: C++(100), Algorithm(99), Advanced Math(99), Linear Algebra(99), \ldots
%  \item I was recommended as postgraduate candidate exempted from GRE (Graduate Record Examination).
%\end{itemize}

\datedsubsection{\textbf{Beihang University (BUAA)}, Beijing, China}{2008 -- 2015 (7 yrs)}
\textit{Master} in Software Engineering.
\textit{Bachelor} in Software Engineering and Applied Mathematics(minor). 
\begin{itemize}
  \item High Scored Courses: C++(100), Algorithm(99), Advanced Math(99), Linear Algebra(99), \ldots
  \item I was recommended as postgraduate candidate exempted from GRE (Graduate Record Examination).
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\awardline{\nth{27} Place}{ACM ICPC World Finals}{2013}
\awardline{\nth{5} Place, Gold Medal}{ACM ICPC Asia Regionals}{2012}
\awardline{Top 500}{Google Code Jam}{2013}
\awardline{Top 500}{Facebook Hacker Cup}{2014}
\awardline{Top 30}{Microsoft Beauty of Programming National Invition Contest}{2013}
\awardline{2 out of 141}{Tencent Scholarship}{2010}
\awardline{6 out of 141}{Outstanding Student Leader}{2008 -- 2009}
\awardline{12 out of 141}{Outstanding Academic Performance Scholarship}{2008 -- 2009}
  %\item \datedline{Beihang Sanguosha 3v3 Match, \textit{\nth{3} Place}}{2013}

% \section{\faUsers\ Experience}
% \datedsubsection{\textbf{FLAG Inc.} California, America}{2012 -- Present}
% \role{Summer Intern}{Manager: xxx}
% Brief introduction: xxx.
% \begin{itemize}
%   \item Implemented xxx feature
%   \item Optimized xxx 5\%
%   \item xxx
% \end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills \& Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Languages: C++11 $>$ English $>$ Python2.7
          	$>$ Java $>$ C\# $>$ SQL $>$ Bash
		%$>$ Matlab/Octave
  %\item Skills: Fast-learning, vim, git, *nix
 % \item Hobbies: Zhihu, Bilibili, Sanguosha; Cycling, Yoga
  %Debug with eyes, Vim, Git 
  % \item Platform: Linux
  % \item Development: Web, xxx
\end{itemize}

\section{Selected Projects at Didi Chuxing}
\datedsubsection{\textbf{Smart Order Distribution (智能分单)}}{Jul.\,2016 -- Present}
 \begin{itemize}
    \item Learns data pattern from previously collected order info to improve matching rates between drivers and passengers. 
          The scale effect of transport capacity is harnessed to maximize overall traffic efficiency and deliver the best travel experience.
    \item We predicted the answer rate for the potential order when the passenger expresses the travel intent, 
          while the result is currently used in dynamic pricing.
 \end{itemize}

\datedsubsection{\textbf{Dynamic Pricing (动态调价)} owner}{Aug.\,2016 -- Present}
 \begin{itemize}
    \item I have refactored to code and added monitor in C++ for Chauffeured Car(专车).
 \end{itemize}

\datedsubsection{\textbf{Passenger Subsidy (乘客补贴)}}{Jul.\,2016 -- Present}
 \begin{itemize}
    \item I built the framework from scratch for the Passenger Subsidy of Chauffeured Car(专车) with playing back support, 
          500 lines of Google-styled C++11 code, thrift server, robust, load balance.
 \end{itemize}

\datedsubsection{\textbf{Transport Capacity Dispatch (运力调度)} owner}{Feb.\,2016 -- Jul.\,2016 (5 mos)}
 \begin{itemize}
    \item Based on the results of supply and demand forecast, 
          all the available transport capacity can be mobilized on a large scale to achieve the best allocation of resources. 
          It also aims to address potential and ongoing supply and demand gap and 
          improves the platform efficiency while leveraging transport capacity to the fullest.
    \item I redesigned and built the new framework for transport capacity dispatch service, 4000 lines of Google-styled C++ code, thrift server.
 \end{itemize}

\datedsubsection{\textbf{Thermodynamic Diagram a.k.a Heatmap (热力图)} owner}{Feb.\,2016 -- Jul.\,2016 (5 mos)}
 \begin{itemize}
    \item Combining analysis result of historical data with real-time order information, 
          the diagram shows places where most orders are concentrated citywide. 
          It aims to provide drivers with valuable reference of order positions 
          so that the probability of calls to be received improves and drivers can minimize their driving time.
    % \item Everyday, the heatmap is viewed $ 7 \times 10^6 $  times by $ 8 \times 10^5 $ drivers.
    \item I added the function to apply configurable different filter on different cities, 
          and launched heatmap in 9 new cities: 
          Shenzhen(深圳), Wuhan(武汉), Tianjin(天津), Zhengzhou(郑州), Nanjing(南京), 
          Chongqing(重庆), Changsha(长沙), Dalian(大连), Fuzhou(福州).
 \end{itemize}

\section{Selected Projects at Microsoft Research Asia}
\datedsubsection{\textbf{Document Rectification}}{Oct.\,2013 -- June.\,2014 (11 mos)}
 \begin{itemize}
    \item Rectify Curved Documents via Robust PCA (Principal Component Analysis) Framework.
    \item Reduce the running time from 100sec to 2sec, in 5,000 lines of C++11 code.
 \end{itemize}

\datedsubsection{\textbf{Click Through Rate Prediction}}{Aug.\,2013 -- Jun.\,2013 (3 mos)}
 \begin{itemize}
    \item Click Through Rate(CTR) Prediction of Bing Search via Logistic Regression(OWLQN) Algorithm.
    \item 2TB data, 2K lines of C++ code, boost, openmp, MPI.
 \end{itemize}

\datedsubsection{\textbf{Text Detection \& Recognization}}{Nov.\,2013 -- Jun.\,2014 (3 mos)}
 \begin{itemize}
    \item Extract textline from raw image.
    \item 1,000 lines of C++11 code, using opencv2.0 and tinyxml library.
 \end{itemize}

\datedsubsection{\textbf{Navigation Robot}}{May.\,2015 -- Jun.\,2015 (2 mos)}
 \begin{itemize}
    \item A navigation robot controlled by a smart phone.
    I added the feature to allow the server to dynamically push runnable code to the phone,
        controling its sensors and bluetooth modulo.
 \end{itemize}

\section{Selected Projects at Parttime}
\datedsubsection{\textbf{Wechat Sync Robot} }{Jun.\,2016 -- Jun.\,2016 (1 mos)}
 \begin{itemize}
    \item A robot that sync the messages between wechat groups for Microsoft Research Asia Alumni.
    \item It allows the 1000+ alumni to chat to each other as if we are in the same group.
    \item It is developed basing on some open source solutions, hacking the web wechat API by packet sniffer.
 \end{itemize}

 
% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
