% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\newcommand{\CC}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}}
\newcommand{\CS}{C\nolinebreak\hspace{-.05em}\raisebox{.6ex}{\scriptsize\bf{\#}}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[L]{\textit{Compiled by \XeLaTeX{}}}
\fancyfoot[R]{Last Modified: \today}
\fancyfoot[C]{}
\fancyhead{}


\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Qingwen GUAN}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in email address
\contactInfo{qingwen.guan@outlook.com}{(+86) 134 0115 7995}{http://lnked.in/qingwen}
% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}

% Experiences表示经历可数，经验不可数
\section{\faUsers\ Long-term Experiences}
\datedsubsection{\textbf{Didi Dache (Xiaojukeji Inc.)} Beijing, China}{2016 -- Present}
\role{Research and Develop Engineer of DiDi Research}{Manager: Jieping YE}
I am in the Dispatch Feature Team, 
working on voice broadcast recommendations, heatmap, data virtualization, and so on.

\datedsubsection{\textbf{Microsoft Inc.} Beijing, China}{2013 -- 2015 (2 yrs)}
\role{Intern of Microsoft Research Asia}{Mentors: Yasuyuki Matsushita, Ambrosio Blanco, \ldots}
I have been working on multiple projects, 
such as Document Rectification, Text Detection, Click Through Rate Prediction, Talking and Dancing Robot.

\section{\faUser\ Short-term Experiences}

\datedsubsection{\textbf{Google Inc.} London, United Kingdom}{Nov.\,2015 -- Jan.\,2016 (3 mos)}
I was in the AGSA team, fixing bugs and refactoring code for the Android App of Google Now.

\datedsubsection{\textbf{Toutiao (Bytedance Inc.)} Beijing, China}{Jul.\,2015 -- Nov.\,2015 (4 mos)}
I was in the internationalization team, building the recommendation system module from scratch. 

\datedsubsection{\textbf{J.P. Morgan Chase} Beijing, China}{Jun.\,2014 -- Oct.\,2014 (3 mos)}
I was in the Quantitative Research team, refactoring code and processing data for internal usage.

\section{\faGraduationCap\ Educations}
\datedsubsection{\textbf{Beihang University (BUAA)}, Beijing, China}{2012 -- 2015 (3 yrs)}
\textit{Master} in Software Engineering.

\datedsubsection{\textbf{Beihang University (BUAA)}, Beijing, China}{2008 -- 2012 (4 yrs)}
\textit{Bachelor} in Software Engineering and Applied Mathematics(minor). 
\begin{itemize}
  \item High Scored Courses: \CC{}(100), Algorithm(99), Advanced Math(99), Linear Algebra(99), \ldots
  \item I was recommended as postgraduate candidate exempted from GRE (Graduate Record Examination).
\end{itemize}


\section{\faHeartO\ Honors and Awards}
\begin{itemize}[parsep=0.5ex]
  \item \datedline{ACM ICPC World Finals, \textit{\nth{27} Place}}{2013}
  \item \datedline{ACM ICPC Asia Regionals, \textit{\nth{5} Place, Gold Medal}}{2012}
  \item \datedline{Google Code Jam, \textit{Top 500}}{2013}
  \item \datedline{Facebook Hacker Cup, \textit{Top 500}}{2014}
  \item \datedline{Microsoft Beauty of Programming National Invition Contest, \textit{Top 30}}{2013}
  \item \datedline{Tencent Scholarship, \textit{2 out of 141}}{2010}
  \item \datedline{Outstanding Student Leader, \textit{6 out of 141}}{2008 -- 2009}
  \item \datedline{Outstanding Academic Performance Scholarship, \textit{12 out of 141}}{2008 -- 2009}
  %\item \datedline{Beihang Sanguosha 3v3 Match, \textit{\nth{3} Place}}{2013}
\end{itemize}

% \section{\faUsers\ Experience}
% \datedsubsection{\textbf{FLAG Inc.} California, America}{2012 -- Present}
% \role{Summer Intern}{Manager: xxx}
% Brief introduction: xxx.
% \begin{itemize}
%   \item Implemented xxx feature
%   \item Optimized xxx 5\%
%   \item xxx
% \end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills \& Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: \CC{} $>$ English $>$ Python2 
          	$>$ Java $>$ \CS{} $>$ SQL $>$ Shell
		%$>$ Matlab/Octave
  \item Skills: Fast-learning, vim, git, *nix
  \item Hobbies: Zhihu, Bilibili, Sanguosha; Cycling, Yoga
  %Debug with eyes, Vim, Git 
  % \item Platform: Linux
  % \item Development: Web, xxx
\end{itemize}

% \section{Selected Projects}
%  \datedsubsection{\textbf{Didi Dache (Xiaojukeji Inc.)} Beijing, China}{2016 -- Present}
% \begin{itemize}
%   \item \datedline{Document Rectification}{Oct.2014 - June.2015 (11 mos)}
%   \item \datedline{Text Detection \& Recognization}{Nov.2013 - Jun.2014 (3 mos)}
%   \item \datedline{Click Through Rate Predict}{Nov.2013 - Jun.2014 (3 mos)}
% \end{itemize}
% 
% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
